\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-14 ms.tex
oh

It is a pleasure to thank
Lauren Anderson (Flatiron),
Ana Bonaca (Harvard),
Elena D'Onghia (UW Madison),
Dan Foreman-Mackey (Flatiron),
Raja Guhathakurta (UCSC),
Cliff Johnson (Northwestern),
Ekta Patel (Arizona),
Sarah Pearson (Flatiron),
Josh Peek (STScI),
Anil Seth (Utah),
and Erik Tollerud (STScI)
for useful suggestions and discussion.

>>>>

It is a pleasure to thank
Lauren Anderson (Flatiron),
Ana Bonaca (Harvard),
Elena D'Onghia (UW Madison),
Dan Foreman-Mackey (Flatiron),
Raja Guhathakurta (UCSC),
Cliff Johnson (Northwestern),
Semyeong Oh (Cambridge),
Ekta Patel (Arizona),
Sarah Pearson (Flatiron),
Josh Peek (STScI),
Anil Seth (Utah),
and Erik Tollerud (STScI)
for useful suggestions and discussion.
